\section{Conclusion}
\label{sec:Conclusion}

The performance for the final Kalman filter based track fit has been evaluated by comparing Monte Carlo truth with reconstructed data, for the key tracker measurements of $x$, $y$, $p_{t}$ and $p_z$.  The observed performance in the transverse position and momentum measurements is excellent, for both the upstream and downstream trackers. The reconstruction resolution in $p_t$ and $p_z$ are within expectation and will provide a sufficient degree of precision for the MICE physics program.

There are however systematic effects present in the momentum reconstruction due to the complexity of precisely modelling the density and thicknesses of the various materials within the tracker. The Monte Carlo model provides a more detailed description than could be feasibly implemented by the reconstruction, hence producing the residuals seen in section~\ref{sec:performance:resolutions}. This discrepancy will be representative of a physical systematic effect in the reconstruction of data and corresponds to the leading systematic effect in the tracker reconstruction.

Monte Carlo studies will be used to model the momentum discrepency and provide a linear correction based on a fit to the data shown in figure~\ref{fig:pBiasKalman}. Comparisons with other detectors in the MICE experiment may provide a data-driven estimate for this correction thereby supporting the Monte Carlo model. In addition it would be possible to further extend the track fit such that an Adaptive Kalman Filter is used, whereby the energy loss per plane is both modelled and estimated by the track fit. Such extensions are currently under discussion.

Due to the precision of the track fit the key measurement of MICE, the transverse emittance of a muon beam, can be very well estimated. The emittance is based on the precise determination of the beam covariance matrix, and is therefore systematically sensitive to the resolution of the reconstruction. The resolutions of the individual parameters are small and symmetric which permits a simple covariance matrix correction to be applied, fully accounting for the measurement effects of the tracker. Additionally, the high resolution reduces the number of muons required to acheive the expected statistical precision of MICE.

